### 2013-06-10 menger.tex
Lots of rothberger stuff, in middle of silly proof

>>>>

  \begin{definition}
    A space $X$ is scattered if every subspace contains an isolated point. By convention, $\ds X = \bigcup_{\alpha<\rank(X)}X^\alpha$ where $X^\alpha$ is the set of isolated points of $\ds X\setminus\bigcup_{\beta<\alpha}X^\beta$.
  \end{definition}

  \begin{proposition}
    A space $X$ is scattered if and only if every closed subspace contains an isolated point.
  \end{proposition}

  \begin{proposition}
    The rank of a compact scattered $T_1$ space is a successor ordinal, and $X^{\rank(X)-1}$ is finite.
  \end{proposition}

  \begin{proof}
    Suppose that the rank of $X$ was a limit ordinal $\beta$. Then by choosing $\beta_n\to\beta$, we may pick a point $x_n\in X^{\beta_n}$, and $\{x_n: n<\omega\}$ may be shown to be a closed discrete subspace of $X$.

    It's easily seen that $X^{\rank(X)-1}$ must be finite - it is a closed discrete subspace of compact $X$.
  \end{proof}

  \begin{theorem}
    The following are equivalent for compact $T_2$ $X$:
      \begin{enumerate}[(a)]
        \item $X$ is Rothberger
        \item $X$ is scattered
        \item $O\win\rothgame{X}$
      \end{enumerate}
  \end{theorem}

  \begin{proof}
    To show $(a)\Rightarrow(b)$, we use Aurichi's proof in \textit{D-Spaces}: suppose $X$ has a closed subspace without isolated points. Then it is compact and contains a closed copy of the Cantor set, which is not Rothberger, contradiction.

    To show $(b)\Rightarrow(c)$, if $X$ is scattered, suppose during a particular round $n$, player $O$ observes that the uncovered subspace $Y \subseteq X$ is nonempty. Then as $Y$ is also compact scattered,  select one of the finite points in $Y^{\rank(Y)-1}$, label it $x_n$, and choose an open set containing $x_n$ from the given cover.

    We claim that if $O$ follows this strategy, player $O$ will observe that the uncovered subspace $Y\subseteq X$ is empty during some round. If not, consider the $x_n$ chosen by $Y$ by the end of the game - the rank of each point within $X$ is nonincreasing, and does not contain a constant final sequence, contradiction.

    Of course, $(c)\Rightarrow(a)$ is trivial.
  \end{proof}

  \begin{theorem}
    The following are equivalent for points-$G_\delta$ $X$:
      \begin{enumerate}[(a)]
        \item $O\win\rothgame{X}$
        \item $O\markwin\rothgame{X}$
        \item $|X|=\omega$
      \end{enumerate}
  \end{theorem}

  \begin{proof}
    $(c)\Rightarrow(b)\Rightarrow(a)$ are all trivial. Galvin has shown $(a)\Rightarrow(c)$ in \textit{Indeterminacy}, but a direct proof follows.

    Suppose $X$ is uncountable: define open sets $G_{x,m}$ for $x\in X$ and $m<\omega$ such that $\{x\}=\bigcap_{m<\omega} G_{x,m}$. Let $\mc{U}_m = \{G_{x,m} : x\in X \}$.
      \[
        A = \{ x \in X : \exists \<m_0,\dots,m_{n-1}\>\in\omega^{<\omega} ( 
          \sigma(\mc{U}_{m_0},\dots,\mc{U}_{m_{n-1}})=G_{x,m_{n-1}} )\}
      \]
    Since $|A|=\omega$, choose $x\in X\setminus A$, and during round $n$, playasdf. TODO finish
  \end{proof}
